A Comparison of Synchronous-CFG \titlelinebreak{} Decoder Implementations

### 2013-07-01 mt-marathon.2013/PBML_article.tex
start adding bibs

% Packages
% ========
% In this place you can load required packages by the \usepackage commands.
% The following packages are loaded automatically by the class:
% euler    (for math fonts)
% graphicx (for inclusion of images)
% multicol (for multicolumn typesetting)
% natbib   (for bibliography citations)
% amssymb  (for various symbols)
% If XeLaTeX is used, fontspec and xltxtra are loaded as well.

@@

This paper describes this new feature function framework as implemented in the Moses decoder, a compares it with that implemented in cdec\cite{Dyer_etal_2010} and Joshua\cite{Joshua-Decoder}.

\section{Feature Function Framework}
\subsection{Old Framework}
The built-in feature functions in the phrase-based models are:

i. Phrase-table

ii. Language model

iii. Distortion model

iii. Lexicalized Reordering model

    iv. Word penalty

    v. Unknown word penalty

The hierarchical and syntax model also uses these models, except for the distortion and lexicalized reordering model.

Each feature function was implemented in a separate class, with no common class hierarchy. The initialisation and evaluation of each feature function was entirely bespoked.

There is also no centralized store of feature functions. A new feature function requires a new variable to store the object.

@@

The state information in Moses has evolved since inception. Initially, state information was only available from language models, therefore, only language models states were compare, Figure (1).

        for each language model state s

>>>>

% Packages
% ========
% In this place you can load required packages by the \usepackage commands.
% The following packages are loaded automatically by the class:
% euler    (for math fonts)
% graphicx (for inclusion of images)
% multicol (for multicolumn typesetting)
% natbib   (for bibliography citations)
% amssymb  (for various symbols)
% If XeLaTeX is used, fontspec and xltxtra are loaded as well.
\usepackage{algorithmic}

@@

This paper describes the changes to the Moses decoder in order to incorporate more feature functions, and compares it with that implemented in cdec\cite{Dyer_etal_2010} and Joshua\cite{Joshua-Decoder}.

\section{Feature Function Framework}
\subsection{Old Framework}

The built-in feature functions in the phrase-based models are:

\begin{itemize}
  \item Translation model
  \item Language model
  \item Distortion model
  \item Lexicalized reordering model
  \item Word penalty
  \item Unknown word penalty
\end{itemize}

The hierarchical and syntax model also uses these feature functions, except for the distortion and lexicalized reordering model.

Each feature function is implemented in a separate class, with no common class hierarchy. The initialisation and evaluation of each feature function was entirely bespoked.

@@

The state information in Moses has evolved since inception. Initially, state information was only available from language models, therefore, only language models states are compared, Figure~\ref{algo:CompareHypoStates}.

\begin{figure} [h!]
\small 
\begin{algorithmic}
\REQUIRE hypothesis $a$, hypothesis b

       \IF {coverage of a != coverage of b }
	\RETURN not equal
       \ENDIF

        \FORALL {LM state s}
          \IF {state s of hypothesis a != state s for hypothesis b}
	    \RETURN not equal
	 \ENDIF
        \ENDFOR
        \RETURN equal

\end{algorithmic}
\caption{Comparing Hypothesis States (old framework}
\label{algo:CompareHypoStates}
\end{figure}
